---
title: "p8105_hw5_sc4935"
author: "Shiwei Chen"
date: "11/17/2021"
output: github_document
---

```{r, message=FALSE}
library(tidyverse)
```

# Problem 1

Raw data is large and some variables are not cleaned.

### Create a city_state variable

```{r}
homicide_df = read_csv("data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, state, sep = ", ")) %>% 
  mutate(solved_or_not = if_else(disposition == "Closed without arrest" | disposition == "Open/No arrest", "unsolved", "solved")) 

homicide_df
```

### Summarize within cities to obtain the total number of homicides and the number of unsolved homicides 

```{r}
homicide_city = homicide_df %>% 
  count(city_state) %>% 
  rename(total = n)
 
homicide_city

homicide_city_unsolved = homicide_df %>% 
  select(city_state, solved_or_not) %>%
  group_by(city_state) %>% 
  summarise(total_unsolved = sum(solved_or_not == "unsolved")) %>% 
  select(-city_state)
  
homicide_city_unsolved 

homicide_count = bind_cols(homicide_city, homicide_city_unsolved) %>% 
  view()
homicide_count
```



### For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved

```{r}
prop.test(
  homicide_count %>% filter(city_state == "Baltimore, MD") %>% pull(total_unsolved), 
  homicide_count %>% filter(city_state == "Baltimore, MD") %>% pull(total)
  ) %>% 
  broom::tidy()

```

### Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each

```{r}
unsolved_prop_city = homicide_count %>% 
  mutate(prop_t = map2(.x = total_unsolved, .y = total, ~prop.test(x = .x, n = .y)), tidy_t = map(.x = prop_t, ~broom::tidy(.x))) %>% 
  unnest(tidy_t) %>% 
  select(city_state, estimate, conf.low, conf.high)
  
unsolved_prop_city
```

### Create a plot that shows the estimates and CIs for each city

```{r}
unsolved_prop_city %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    title = "The estimates and CIs for each city",
    x = "City of state",
    y = "Estimate rate",
    caption = "Data from homicide-data.csv"
  )

```






# Problem 2

### Start with a dataframe containing all file names

```{r, error = TRUE, message=FALSE}
path_df = tibble(path = list.files("data/data_p2/")) %>% 
  mutate(path = str_c("data/data_p2/", path), data = map(.x = path, read_csv))
read_csv(path_df$path[[20]])

research_df = path_df %>% 
  unnest(data)

research_df
```

### Tidy the result

```{r}
research_tidy = research_df %>% 
  rename(arm_type = path) %>% 
  mutate(arm_type = str_replace(arm_type, "data/data_p2/", "")) %>% 
  mutate(arm_type = str_replace(arm_type, ".csv", "")) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "observations") %>% 
  mutate(week = str_replace(week, "week_", "")) %>% 
  separate(arm_type, into = c("arm", "id"), sep = "_") %>% 
  mutate(arm = recode(arm, "con" = "control", "exp" = "experimental")) %>% 
  arrange(arm, id, week) 
  
research_tidy
```

### Make a spaghetti plot showing observations on each subject over time

```{r}
ggplot(research_tidy, aes(x = week, y = observations, color = id, group = id)) +
  geom_line() + facet_grid(. ~ arm) +
  labs(
    title = "Observations on each subject over time",
    x = "Week",
    y = "Observation value"
  )
```

### Comment on differences between groups

Compare the experimental group to the control group, the trend of the experimental group shows strong positive correlation(observations of each subject increase over time) for the observations on each subject over time. For the trend of the control group, the plot indicates very weak correlation for the observations on each subject over time.



# Problem 3

Load the iris dataset

```{r}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species)) 

iris_with_missing
```

Write two cases of functions

```{r}
iris_wo_missing = function(vec) {
  if (is.numeric(vec)) {
    replace_na(vec, round(mean(vec, na.rm = TRUE), digits = 1))
    }
  else if (is.character(vec)) {
    replace_na(vec, "virginica")
    }
} 
```

### Apply this function to the columns of iris_with_missing using a map statement
 
```{r}
map_df(iris_with_missing, iris_wo_missing) 
```
